---
title: "Burden"
output: html_document
fontsize: 2pt
---

Use SPIDEX to predict how an SNV affects splicing
Put SPIDEX the highest priority.
Directly use ANNOVAR output to annotate syn and nonysno, without only using mutations that overlap with genes that are in the list of genes with synonymous mutation rates. 

non ASD genes are the bottom 20%
not plotting mutation is 5'UTR or 3'UTR

```{r}
getwd()
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```
### read in coding tada data

```{r,echo=FALSE}
getwd()
# need to set this direcoty to full direcoty of ASD/analysis
coding_tada = read.delim("../other_annotation/gene_list/TADA_SNV_CNV_combined_Feb7.txt", header = TRUE, sep = "\t", stringsAsFactors = FALSE)
coding_tada_denovo = data.frame(coding_tada$RefSeqName, coding_tada$TadaName, coding_tada$mut.rate, coding_tada$dn.LoF, coding_tada$dn.mis3, coding_tada$BF.SNV.dn, coding_tada$BF.combined, coding_tada$qvalue.combined)
colnames(coding_tada_denovo) = c("RefSeqName", "TadaName", "mut.rate", "dn.LoF", "dn.mis3", "BF.SNV.dn", "BF.combined", "qvalue.combined")

#read in workspace that has unique mutation information
mutation = new.env()
load("../data/debug_region_list_073116_data_matrixtransformed_for_old_code.Rdata", envir = mutation)
write.table(mutation$mutation[,1:4],"160229_data_for_analysis.bed",col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE)

# load releant functions
source("../lib/160930_screen_burden_functions_test_more_genelist_focused.R")

```


### get SPIDEX value ###
```{r,cache=TRUE}
SPIDEX = generate_spidex_score(mutation$mutation, mutation$ref_alt_allele)
```

### synonymous mutation number ins cases and controls
```{r}
mutation$syn_number_ASD
mutation$syn_number_control
length(mutation$ASD_effective_SNV_ID)
length(mutation$control_effective_SNV_ID)

```
### potential for disrupting splicing, lower than 20%
```{r}
knitr::kable(show_burden_for_SPIDEX(quantile(SPIDEX$dpsi_zscore,seq(0,1,0.1),na.rm = TRUE)[1],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.1),na.rm = TRUE)[3],syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control))
```

### lower than 10%
```{r}
knitr::kable(show_burden_for_SPIDEX(quantile(SPIDEX$dpsi_zscore,seq(0,1,0.1),na.rm = TRUE)[1],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.1),na.rm = TRUE)[2],syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control))
```

```{r}
knitr::kable(get_mutations_with_spidex2_geneset(SPIDEX, quantile(SPIDEX$dpsi_zscore,seq(0,1,0.1),na.rm = TRUE)[1],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.1),na.rm = TRUE)[2], stringent_ASD),syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control)
```

### lower than 5 percent
```{r}
knitr::kable(show_burden_for_SPIDEX(quantile(SPIDEX$dpsi_zscore,seq(0,1,0.05),na.rm = TRUE)[1],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.05),na.rm = TRUE)[2], syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control))
```

### lower than 2.5 percent
```{r}
knitr::kable(show_burden_for_SPIDEX(quantile(SPIDEX$dpsi_zscore,seq(0,1,0.025),na.rm = TRUE)[1],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.025),na.rm = TRUE)[2], syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control))
```


### Middle 45% to 55%
```{r}
knitr::kable(show_burden_for_SPIDEX(quantile(SPIDEX$dpsi_zscore,seq(0,1,0.025),na.rm = TRUE)[19],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.025),na.rm = TRUE)[23], syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control))
```

### Middle 40% to 60%
```{r}
knitr::kable(show_burden_for_SPIDEX(quantile(SPIDEX$dpsi_zscore,seq(0,1,0.025),na.rm = TRUE)[17],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.025),na.rm = TRUE)[25], syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control))
```


### potential for disrupting splicing, higher than 80% 
```{r}
knitr::kable(show_burden_for_SPIDEX(quantile(SPIDEX$dpsi_zscore,seq(0,1,0.1),na.rm = TRUE)[9],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.1),na.rm = TRUE)[11], syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control))
```

### higher than 90%
```{r}
knitr::kable(show_burden_for_SPIDEX(quantile(SPIDEX$dpsi_zscore,seq(0,1,0.1),na.rm = TRUE)[10],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.1),na.rm = TRUE)[11], syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control))
```

### higher than 95%
```{r}
knitr::kable(show_burden_for_SPIDEX(quantile(SPIDEX$dpsi_zscore,seq(0,1,0.05),na.rm = TRUE)[20],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.05),na.rm = TRUE)[21], syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control))
```

### higher than 97.5%
```{r}
knitr::kable(show_burden_for_SPIDEX(quantile(SPIDEX$dpsi_zscore,seq(0,1,0.025),na.rm = TRUE)[40],quantile(SPIDEX$dpsi_zscore,seq(0,1,0.025),na.rm = TRUE)[41], syn_ASD = mutation$syn_number_ASD, syn_control = mutation$syn_number_control))
```

