---
title: "Burden"
output: pdf_document
fontsize: 2pt
---


Partition enhancers based on distance to TSS based on strict overlap. 
Basically, her pipeline takes intersections between enhancers and distance ranges, and remove bases of enhancers that are not overlapped. 
### NOTICE


```{r}
getwd()
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

### read in data with predicted mutation count and observed mutation count
```{r,echo=FALSE}
load("161120_mutation_rate_calibration_sum_per_gene_with_Noonan_brain_roadmap_union_1bp_overlap.Rdata")
```

### load in functions and datastes that make the functions work
```{r,echo=FALSE}
coding_tada = read.delim("../other_annotation/gene_list/TADA_SNV_CNV_combined_Feb7.txt", header = TRUE, sep = "\t", stringsAsFactors = FALSE)
coding_tada_denovo = data.frame(coding_tada$RefSeqName, coding_tada$TadaName, coding_tada$mut.rate, coding_tada$dn.LoF, coding_tada$dn.mis3, coding_tada$BF.SNV.dn, coding_tada$BF.combined, coding_tada$qvalue.combined)
colnames(coding_tada_denovo) = c("RefSeqName", "TadaName", "mut.rate", "dn.LoF", "dn.mis3", "BF.SNV.dn", "BF.combined", "qvalue.combined")

#read in workspace that has unique mutation information
mutation = new.env()
load("../data/debug_region_list_073116_data_matrixtransformed_for_old_code.Rdata", envir = mutation)
write.table(mutation$mutation[,1:4],"160229_data_for_analysis.bed",col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE)
# load releant functions
source("../lib/160930_screen_burden_functions_test_more_genelist_focused.R")
```

### ASD manuscript data, stringent ASD genes
```{r,echo=FALSE}
predicted = sum(ASD_model_manuscript_mutrate$enhancer[is.element(ASD_model_manuscript_mutrate$enhancer$genename, stringent_ASD),]$adjusted_mutrate_sum)
observed = sum(ASD_model_manuscript_mutrate$enhancer[is.element(ASD_model_manuscript_mutrate$enhancer$genename, stringent_ASD),]$mut_count_sum)
# strigent ASD genes

```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```

### ASD manuscript data, relaxed ASD genes
```{r,echo=FALSE}
predicted = sum(ASD_model_manuscript_mutrate$enhancer[is.element(ASD_model_manuscript_mutrate$enhancer$genename, relaxed_ASD),]$adjusted_mutrate_sum)
observed = sum(ASD_model_manuscript_mutrate$enhancer[is.element(ASD_model_manuscript_mutrate$enhancer$genename, relaxed_ASD),]$mut_count_sum)
# strigent ASD genes

```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```

### control_model_693_mutrate data, stringent ASD genes
```{r,echo=FALSE}
predicted = sum(control_model_693_mutrate$enhancer[is.element(control_model_693_mutrate$enhancer$genename, stringent_ASD),]$adjusted_mutrate_sum)
observed = sum(control_model_693_mutrate$enhancer[is.element(control_model_693_mutrate$enhancer$genename, stringent_ASD),]$mut_count_sum)
# strigent ASD genes

```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```

### control_model_693_mutrate, relaxed ASD genes
```{r,echo=FALSE}
predicted = sum(control_model_693_mutrate$enhancer[is.element(control_model_693_mutrate$enhancer$genename, relaxed_ASD),]$adjusted_mutrate_sum)
observed = sum(control_model_693_mutrate$enhancer[is.element(control_model_693_mutrate$enhancer$genename, relaxed_ASD),]$mut_count_sum)
# strigent ASD genes

```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```

### control_model_258_mutrate data, stringent ASD genes
```{r,echo=FALSE}
predicted = sum(control_model_258_mutrate$enhancer[is.element(control_model_258_mutrate$enhancer$genename, stringent_ASD),]$adjusted_mutrate_sum)
observed = sum(control_model_258_mutrate$enhancer[is.element(control_model_258_mutrate$enhancer$genename, stringent_ASD),]$mut_count_sum)
# strigent ASD genes

```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```

### control_model_258_mutrate, relaxed ASD genes
```{r,echo=FALSE}
predicted = sum(control_model_258_mutrate$enhancer[is.element(control_model_258_mutrate$enhancer$genename, relaxed_ASD),]$adjusted_mutrate_sum)
observed = sum(control_model_258_mutrate$enhancer[is.element(control_model_258_mutrate$enhancer$genename, relaxed_ASD),]$mut_count_sum)
# strigent ASD genes

```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```

### ASD_model_Scherer_mutrate data, stringent ASD genes
```{r,echo=FALSE}
predicted = sum(ASD_model_Scherer_mutrate$enhancer[is.element(ASD_model_Scherer_mutrate$enhancer$genename, stringent_ASD),]$adjusted_mutrate_sum)
observed = sum(ASD_model_Scherer_mutrate$enhancer[is.element(ASD_model_Scherer_mutrate$enhancer$genename, stringent_ASD),]$mut_count_sum)
# strigent ASD genes

```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```

### ASD_model_Scherer_mutrate, relaxed ASD genes
```{r,echo=FALSE}
predicted = sum(ASD_model_Scherer_mutrate$enhancer[is.element(ASD_model_Scherer_mutrate$enhancer$genename, relaxed_ASD),]$adjusted_mutrate_sum)
observed = sum(ASD_model_Scherer_mutrate$enhancer[is.element(ASD_model_Scherer_mutrate$enhancer$genename, relaxed_ASD),]$mut_count_sum)
# strigent ASD genes

```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```


