---
title: "Burden"
output: pdf_document
fontsize: 2pt
---


Only count synonymous mutations identified by Annovar that are in the coding regions used in model training.
Notice that in model training, promoter regions have a higher priority than coding regions. 
LoF here is stop gain, frameshift insertion and frameshift deletion.


```{r}
getwd()
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

### read in data with predicted mutation count and observed mutation count
```{r,echo=FALSE}
load("161120_mutation_rate_calibration_sum_per_gene_with_Noonan_brain_roadmap_union_1bp_overlap.Rdata")
```

### load in functions and datastes that make the functions work
```{r,echo=FALSE}
coding_tada = read.delim("../other_annotation/gene_list/TADA_SNV_CNV_combined_Feb7.txt", header = TRUE, sep = "\t", stringsAsFactors = FALSE)
coding_tada_denovo = data.frame(coding_tada$RefSeqName, coding_tada$TadaName, coding_tada$mut.rate, coding_tada$dn.LoF, coding_tada$dn.mis3, coding_tada$BF.SNV.dn, coding_tada$BF.combined, coding_tada$qvalue.combined)
colnames(coding_tada_denovo) = c("RefSeqName", "TadaName", "mut.rate", "dn.LoF", "dn.mis3", "BF.SNV.dn", "BF.combined", "qvalue.combined")

#read in workspace that has unique mutation information
mutation = new.env()
load("../data/debug_region_list_073116_data_matrixtransformed_for_old_code.Rdata", envir = mutation)

source("../lib/160930_screen_burden_functions_test_more_genelist_focused.R")

source("../lib/161117_glm_for_mutation_count.R")

```



### ASD manuscript data
```{r}
mutation = new.env()
load("../data/debug_region_list_073116_data_matrixtransformed_for_old_code.Rdata", envir = mutation)
coding_data_count = get_coding_mut_number(mutation$mutation, mutation$ref_alt_allele, "../other_annotation/epigenomic_annotation/Whole_genome.promoter_yanyu_10kb_exons_no_utr_no_na_genes.50bp_window.bed", "/media/yuwen/Elements/ANNOVAR/annovar/", "ASD","no")
compare_pre_with_obs(ASD_model_manuscript_mutrate$coding, coding_data_count$coding_mut_for_gene, geneset = c("stringent_ASD", "relaxed_ASD", "nonASD_genes","constraint_union"), mutation_type = c("synonymous", "nonsynonymous", "LoF"), 
                                 mutation_scailing = list(synonymous = 0.2, nonsynonymous = 0.5, LoF = 0.01))

```


### control_model_693_mutrate
```{r,echo=FALSE}
mutation = new.env()
load("../data/debug_region_list_073116_data_matrixtransformed_for_old_code.Rdata", envir = mutation)
coding_data_count = get_coding_mut_number(mutation$mutation, mutation$ref_alt_allele, "../other_annotation/epigenomic_annotation/Whole_genome.promoter_yanyu_10kb_exons_no_utr_no_na_genes.50bp_window.bed", "/media/yuwen/Elements/ANNOVAR/annovar/", "control","no")
compare_pre_with_obs(control_model_693_mutrate$coding, coding_data_count$coding_mut_for_gene, geneset = c("stringent_ASD", "relaxed_ASD", "nonASD_genes","constraint_union"), mutation_type = c("synonymous", "nonsynonymous", "LoF"), 
                                 mutation_scailing = list(synonymous = 0.2, nonsynonymous = 0.5, LoF = 0.01))

```

### control_258_model, 
```{r,echo=FALSE}
mutation = new.env()
load("../data/debug_region_list_073116_using_258_control_data_matrixtransformed_for_old_code.Rdata", envir = mutation)
coding_data_count = get_coding_mut_number(mutation$mutation, mutation$ref_alt_allele, "../other_annotation/epigenomic_annotation/Whole_genome.promoter_yanyu_10kb_exons_no_utr_no_na_genes.50bp_window.bed", "/media/yuwen/Elements/ANNOVAR/annovar/", "control","no")
compare_pre_with_obs(control_model_258_mutrate$coding, coding_data_count$coding_mut_for_gene, geneset = c("stringent_ASD", "relaxed_ASD", "nonASD_genes","constraint_union"), mutation_type = c("synonymous", "nonsynonymous", "LoF"), 
                                 mutation_scailing = list(synonymous = 0.2, nonsynonymous = 0.5, LoF = 0.01))

```

### Scherer case data
```{r,echo=FALSE}
mutation = new.env()
load("../data/161026_Stephen_Scherer_Gemomic_Medicine_ASD_de_novo_SNVs_germline_with_NC_control_data_matrixtransformed_for_old_code.Rdata", envir = mutation)
coding_data_count = get_coding_mut_number(mutation$mutation, mutation$ref_alt_allele, "../other_annotation/epigenomic_annotation/Whole_genome.promoter_yanyu_10kb_exons_no_utr_no_na_genes.50bp_window.bed", "/media/yuwen/Elements/ANNOVAR/annovar/", "ASD","no")
compare_pre_with_obs(ASD_model_Scherer_mutrate$coding, coding_data_count$coding_mut_for_gene, geneset = c("stringent_ASD", "relaxed_ASD", "nonASD_genes","constraint_union"), mutation_type = c("synonymous", "nonsynonymous", "LoF"), 
                                 mutation_scailing = list(synonymous = 0.2, nonsynonymous = 0.5, LoF = 0.01))

```
