---
title: "Untitled"
author: "Yuwen"
date: "January 24, 2017"
output: html_document
---

```{r}
set.seed(100)
source("../lib/170122_base_level_simulation_functions.R")
```


##### generate a dataset with 1e5 bases, effect size 3
```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(2e5,base_mutrate = 1e-4, effect = 3)
cate <- adjust_muatation_rate_optimization_test_simple_categorization(data)
dim(data)
```

```{r}
cate
```

##### generate a dataset with 1e5 bases, effect size 1, using Version V3 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v3, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple, dependson = data}
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v3(data)
dim(data)
```

```{r}
cate
```

##### generate a dataset with 1e5 bases, effect size 1, using optimization but without categorization

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_without_categorization, dependson=data}
cate <- adjust_muatation_rate_optimization_test_simple_without_categorization(data)
dim(data)
```

```{r}
cate
```

##### generate a dataset with 1e5 bases, effect size 3
```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(0.5e5,base_mutrate = 1e-4, effect = 3)
cate <- adjust_muatation_rate_optimization_test_simple_categorization(data)
dim(data)
```

```{r}
cate
```

##### generate a dataset with 1e5 bases, effect size 1, using Version V3 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v3, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple, dependson = data}
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v3(data)
dim(data)
```

```{r}
cate
```

##### generate a dataset with 1e5 bases, effect size 1, using optimization but without categorization

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_without_categorization, dependson=data}
cate <- adjust_muatation_rate_optimization_test_simple_without_categorization(data)
dim(data)
```

```{r}
cate
```
