---
title: "Burden"
output: pdf_document
fontsize: 2pt
---


Partition enhancers based on distance to TSS based on strict overlap. 
Basically, her pipeline takes intersections between enhancers and distance ranges, and remove bases of enhancers that are not overlapped. 
Will not use any epigenomic annotations during mutation rate adjustment.


```{r}
getwd()
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
source("../lib/161117_glm_for_mutation_count.R")
```

```{r, echo=FALSE, cache=TRUE, cache.extra=predict_sum_mutation_rate_per_gene_v2}
prefix <-system("date +%s", intern = TRUE) # prefix for temporary files that will be deleted at the end of the pipeline
new_control = new.env()
load("../data/debug_region_list_073116_using_258_control_data_matrix.Rdata", new_control)
write.table(new_control$data_matrix[new_control$data_matrix$Prediction == "dnv_proband" & new_control$data_matrix$Type == "SNV",c(1,2,3,7)], paste(prefix,"temp.bed",sep = ""), col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE)

ASD_model_manuscript_mutrate = predict_sum_mutation_rate_per_gene_v2(paste(prefix,"temp.bed",sep = ""), "../other_annotation/epigenomic_annotation/Whole_genome.promoter_yanyu_10kb_exons_no_utr_no_na_genes.50bp_window.bed",
                                         "../other_annotation/epigenomic_annotation/Whole_genome.promoter_yanyu_10kb_exons_no_utr_no_na_genes.50bp_window.bed.fasta.cg",
                                         "../other_annotation/epigenomic_annotation/Whole_genome.promoter_yanyu_10kb_exons_no_utr_no_na_genes.50bp_window.bed.mutrate",
                                         314,
                                         "../other_annotation/epigenomic_annotation/Noonan_brain_roadmap_union.bed",
                                         1e-9,
                                         "../other_annotation/epigenomic_annotation/Whole_genome.promoter_yanyu_10kb_exons_no_utr_no_na_genes.50bp_window.bed_genename.bed")

rm(new_control)
system(paste("rm ",prefix,"annovar_input_temp.bed",sep = ""))
system(paste("rm ",prefix, "temp.bed",sep = ""))
```


### load in functions and datastes that make the functions work
```{r,echo=FALSE}
coding_tada = read.delim("../other_annotation/gene_list/TADA_SNV_CNV_combined_Feb7.txt", header = TRUE, sep = "\t", stringsAsFactors = FALSE)
coding_tada_denovo = data.frame(coding_tada$RefSeqName, coding_tada$TadaName, coding_tada$mut.rate, coding_tada$dn.LoF, coding_tada$dn.mis3, coding_tada$BF.SNV.dn, coding_tada$BF.combined, coding_tada$qvalue.combined)
colnames(coding_tada_denovo) = c("RefSeqName", "TadaName", "mut.rate", "dn.LoF", "dn.mis3", "BF.SNV.dn", "BF.combined", "qvalue.combined")

#read in workspace that has unique mutation information
mutation = new.env()
load("../data/debug_region_list_073116_data_matrixtransformed_for_old_code.Rdata", envir = mutation)
write.table(mutation$mutation[,1:4],"160229_data_for_analysis.bed",col.names = FALSE, row.names = FALSE, sep = "\t", quote = FALSE)
# load releant functions
source("../lib/160930_screen_burden_functions_test_more_genelist_focused.R")
```


### ASD manuscript data, active enhancers
```{r,echo=FALSE}
predicted = sum(ASD_model_manuscript_mutrate$enhancer$adjusted_mutrate_sum)
observed = sum(ASD_model_manuscript_mutrate$enhancer$mut_count_sum)
```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```

### ASD manuscript data, active promoters
```{r,echo=FALSE}
predicted = sum(ASD_model_manuscript_mutrate$promoter$adjusted_mutrate_sum)
observed = sum(ASD_model_manuscript_mutrate$promoter$mut_count_sum)
```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```

### ASD manuscript data, coding
```{r,echo=FALSE}
predicted = sum(ASD_model_manuscript_mutrate$coding$adjusted_mutrate_sum)
observed = sum(ASD_model_manuscript_mutrate$coding$mut_count_sum)
```

```{r}
predicted
observed
ppois(observed-1, predicted,lower.tail = FALSE)
```



