```{r}
set.seed(100)
source("../lib/170122_base_level_simulation_functions.R")
```

##### base-level simulation and optimization of mutation rate adjustion parameters using optim() without categorization
```
Assume 1 binary variables (e.g., epigenomic annotations) affect the observed mutation pattern.
Assume baselevel mutation rate is 1e-4 for every base. 

```

##### generate a dataset with 1e6 bases, effect size 3
```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(1e6,base_mutrate = 1e-4, effect = 3)
cate <- adjust_muatation_rate_optimization_test_simple_categorization(data)
glm <- adjust_muatation_rate_optimization_test_simple_glm(data)
```

```{r}
cate
glm
```


##### generate a dataset with 5e6 bases, effect size 3
```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(5e6,base_mutrate = 1e-4, effect = 3)
cate <- adjust_muatation_rate_optimization_test_simple_categorization(data)
glm <- adjust_muatation_rate_optimization_test_simple_glm(data)
```

```{r}
cate
glm
```


##### generate a dataset with 1e7 bases, effect size 1
```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(1e7,base_mutrate = 1e-4, effect = 1)
cate <- adjust_muatation_rate_optimization_test_simple_categorization(data)
glm <- adjust_muatation_rate_optimization_test_simple_glm(data)
rm(data)
```

```{r}
cate
glm
```

##### generate a dataset with 1e7 bases, effect size 1, using Version 2 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v2, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(1e7,base_mutrate = 1e-4, effect = 1)
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v2(data)
rm(data)
```

```{r}
cate
```


##### generate a dataset with 5e6 bases, effect size 3, using Version 2 categorization function
```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v2, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(5e6,base_mutrate = 1e-4, effect = 3)
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v2(data)
```

```{r}
cate
```

##### generate a dataset with 1e7 bases, effect size 1, using Version 1 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(1e7,base_mutrate = 1e-4, effect = 1)
cate <- adjust_muatation_rate_optimization_test_simple_categorization(data)
rm(data)
```

```{r}
cate
```

##### generate a dataset with 1e7 bases, effect size 3, using Version 1 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(1e7,base_mutrate = 1e-4, effect = 3)
cate <- adjust_muatation_rate_optimization_test_simple_categorization(data)
```

```{r}
cate
```

##### generate a dataset with 1e7 bases, effect size 3, using Version 2 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v2, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v2(data)
```

```{r}
cate
```

##### generate a dataset with 1e7 bases, effect size 3, using Version 2_temp function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v2_temp, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v2_temp(data)
```

```{r}
cate
```

##### generate a dataset with 3e7 bases, effect size 3, using Version 2 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v2_temp, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}

data <- sim_table_simple(3e7,base_mutrate = 1e-4, effect = 3)
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v2(data)
```

```{r}
cate
```

##### generate a dataset with 3e7 bases, effect size 3, using Version 2_temp function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v2_temp, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v2_temp(data)
```

```{r}
cate
```

##### generate a dataset with 3e7 bases, effect size 3, using Version V3 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v3, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v3(data)
```

```{r}
cate
```

##### generate a dataset with 1e7 bases, effect size 1
```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(1e7,base_mutrate = 1e-4, effect = 1)
cate <- adjust_muatation_rate_optimization_test_simple_categorization(data)
glm <- adjust_muatation_rate_optimization_test_simple_glm(data)
```

```{r}
cate
glm
```

##### generate a dataset with 1e7 bases, effect size 1, using Version V3 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v3, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v3(data)
```

```{r}
cate
```

##### generate a dataset with 1e7 bases, effect size 1
```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(1e7,base_mutrate = 1e-4, effect = 1)
cate <- adjust_muatation_rate_optimization_test_simple_categorization(data)
glm <- adjust_muatation_rate_optimization_test_simple_glm(data)
```

```{r}
cate
glm
```

##### generate a dataset with 1e7 bases, effect size 1, using Version V3 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v3, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v3(data)
```

```{r}
cate
```

##### generate a dataset with 1e7 bases, effect size 1, using optimization but without categorization

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_without_categorization}
cate <- adjust_muatation_rate_optimization_test_simple_without_categorization(data)
```

```{r}
cate
```

##### generate a dataset with 5e7 bases, effect size 1
```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
data <- sim_table_simple(5e7,base_mutrate = 1e-4, effect = 1)
cate <- adjust_muatation_rate_optimization_test_simple_categorization(data)
```

```{r}
cate
```

##### generate a dataset with 5e7 bases, effect size 1, using Version V3 function

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_categorization_v3, cache.extra = adjust_muatation_rate_optimization_test_simple_glm, cache.extra = sim_table_simple}
cate <- adjust_muatation_rate_optimization_test_simple_categorization_v3(data)
```

```{r}
cate
```

##### generate a dataset with 5e7 bases, effect size 1, using optimization but without categorization

```{r, cache=TRUE, cache.extra = adjust_muatation_rate_optimization_test_simple_without_categorization}
cate <- adjust_muatation_rate_optimization_test_simple_without_categorization(data)
```

```{r}
cate
```
